  \item {Xingfei Wei, Yinong Zhao, Yi Zhuang, and Rigoberto Hernandez. 
``Building Blocks for Autonomous Computing Materials: Dimers, Trimers and Tetramers.''
J. Chem. Phys. 155, 154704 (2021).}
  \item {Xingfei Wei, Yinong Zhao, Yi Zhuang, and Rigoberto Hernandez. 
``Engineered Nanoparticle Network Models for Autonomous Computing.''
J. Chem. Phys. 154, 214702 (2021).}
  \item {Xingfei Wei, Zihan Huang, Stephen Koch, Massimiliano Zamengo, Yichen Deng, Marilyn L. Minus, Junko Morikawa, Ruilan Guo, and Tengfei Luo. 
``Thermal Conductivity of Pentiptycene-based Poly(o-hydroxyimide) Copolymers: A Study via Integrated Experiments and Simulations.'' 
ACS Appl. Polym. Mater. 3, 2979--2987 (2021).}
  \item {Xingfei Wei, Zhi Wang, Zhiting Tian, and Tengfei Luo. 
``Thermal Transport in Polymers: A Review.'' 
J. Heat Transfer 143, 072101 (2021).}
  \item {Xingfei Wei, Ruimin Ma, and Tengfei Luo. 
``Thermal Conductivity of Polyelectrolytes with Different Counterions.'' 
ACS J. Phys. Chem. C. 124, 4483--4488 (2020).}
  \item {Xingfei Wei and Tengfei Luo. 
``Chain Length Effect on Thermal Transport in Amorphous Polymers and A Structure-Thermal Conductivity Relation.''
Phys. Chem. Chem. Phys. 21, 15523--15530 (2019).}
  \item {Xingfei Wei and Tengfei Luo. 
``A Phonon Wave Packet Study of Thermal Energy Transport across Functionalized Hard-Soft Interfaces.'' 
J. Appl. Phys. 126, 015301 (2019).}
  \item {Xingfei Wei and Tengfei Luo. 
``Role of Ionization in Thermal Transport of Solid Polyelectrolytes.'' 
ACS J. Phys. Chem. C. 123, 12659--12665 (2019).}
  \item {Xingfei Wei and Tengfei Luo. 
``The Effect of Block Ratio on the Thermal Conductivity of Amorphous Polyethylene-Polypropylene (PE-PP) Diblock Copolymers.''
Phys. Chem. Chem. Phys. 20, 20534--20539 (2018).}
  \item {Xingfei Wei and Tengfei Luo. 
``Effects of Electrostatic Interaction and Chirality on the Friction Coefficient of Water Flow Inside Single-Walled Carbon Nanotubes and Boron Nitride Nanotubes.''
ACS J. Phys. Chem. C. 122, 5131--5140 (2018).}
  \item {Xingfei Wei, Teng Zhang, and Tengfei Luo. 
``Thermal Energy Transport across Hard-Soft Interfaces.''
ACS Energy Lett. 2, 2283--2292 (2017).}
  \item {}
  \item {Xingfei Wei, Teng Zhang, and Tengfei Luo. 
``Chain Conformation-Dependent Thermal Conductivity of Amorphous Polymer Blends: the Impact of Inter- and Intra-Chain Interactions.''
Phys. Chem. Chem. Phys. 18, 32146--32154 (2016).}
  \item {Vinith Bejugam, Xingfei Wei, and D. K. Roper. 
``Reductive Spectrophotometry of Divalent Tin Sensitization on Soda Lime Glass.''
Appl. Surf. Sci. 376, 43--51 (2016).}
  \item {Xingfei Wei, G. Jang, and D. K. Roper. 
``Spectrophotometric Method for the Determination of Tin(II) by Redox Reaction using 3,3',5,5'-tetramethylbenzidine dihydrochloride and N-bromosuccinimide.'' 
J. Anal. Chem. 70, 566--572 (2015).}
  \item {}
  \item {M. Lisunova, Justin Norman, Xingfei Wei, Samir Jenkins, Jingyi Chen, and D. K. Roper. 
``Aqueous Dispersion of Plasmonic Hollow Metal Nanoparticles.''
Mater. Lett. 117, 241--243 (2014).}
  \item {M. Lisunova, Xingfei Wei, D. DeJarnette, G. T. Forcherio, K. Berry, P. Blake, and D. K. Roper. 
``Photothermal Response of Plasmonic Nanoconglomerates in Assembled Films by Electroless Plating.'' 
RSC Adv. 4, 20894--20901 (2014).}



  \item {Yinong Zhao, Xingfei Wei, Yi Zhuang, and Rigoberto Hernandez. ``Neuromorphic Computing Primitives Using Polymer-Networked Nanoparticles.'' Revised and resubmitted.}
 \item {Gene Chong, Udaya Dahal, Wandi Xu, Xingfei Wei, Qiang Cui, and Rigoberto Hernandez. ``Structural and Dynamical Consistency in Vesicles across All-Atom, MARTINI, and Dissipative.'' In revising and to be resubmitted.}
  \item {Xingfei Wei, Qiankun Mo, Chi Chen, Mark Bathe, and Rigoberto Hernandez. ``Convolutional Neural Networks (CNNs) for DNA Origami Cluster Classification.'' In preparation.}
  \item {Xingfei Wei, Maitreyee, and Rigoberto Hernandez. ``Review in Computational Tools for Materials Design.'' in preparation for ACS Chemical Reviews. In preparation.}
  \item {Ewa Harazinska, Xingfei Wei, and Rigoberto Hernandez. ``Combinatorial Threshold-Linear Network Model for Simulating Information Storage in Engineered Nanoparticle Networks.'' In preparation.}
 \item {Xingfei Wei, Ruilan Guo, and Tengfei Luo. ``A Computational Method for Calculating Gas Diffusivity, Solubility and Permeability in Pentiptycene-based Poly(o-hydroxyimide) Copolymers.'' In preparation.}